A flexible framework to prototype, develop and manage ubiquitous applications for intelligent environments

### 2013-10-03  labtempo-ubicomp-projects/UbicompMiddleware/doc/PerCom2014/percom2014_conf.tex
written about security service "finalization" of example applications changed location of communication text, which went to SMartAndroid

The decentralization of components of the framework (the RAs) follow the principles of the Service-oriented Architecture (SoA), where the more decentralization the more flexibility on connectivity, since the dependence of centralized services is lowered.
%TODO: write it better

@@

    \subsubsection{Security Management Service}
    The security concern is always a central topic on UbiComp systems, moreover because of diverse aspects of security required. Some aspects are already inherited depending on the technology adopted, e.t., the Wi-Fi already ensures against the registration of outside devices and the exchange of informations.

    [credentials]

    [domains]
    % The SecMS manages both the user's credentials and the application's domains.
    % 
    % On the

  \subsection{Context Interpretation} \label{subsec:ci}
  [motivation]

@@

  An example of context rules has been presented on Figure~\ref{fig:arch}. At the Applications Layer a set of two components implements the interpretation-actuation pattern: the ``Forgotten Stove Interpreter'' and the ``Reminder Actuator'' respectively, where the goal of the rule is to remind the elderly that he has forgotten the oven on while he went to sleep. The former component, which is a CI, is subscribed to two RAs, namely the ``Bed RA'' and the ``Stove RA'' (the dashed arrow means notify subscriptors). The latter is subscribed to the CI and calls the RAs, namely the ``TV RA'' and the ``Clock RA'', directly using RPC (represented by the straight arrow). Internally to the CI a rule expression relates the RAs as  ``bed is occupied and oven is turned on for 30 min'', which means that the CI only will be valid if this condition remains true during ``30 min''. When the CI changes its state from invalid to valid (what includes the timing), the subscriptors are notified, the ``Reminder Actuator'' in case. This actuator, in its turn, calls the OPs ``fire alarm'' from ``Clock RA'' and ``set message'' from ``TV RA'', with the parameter ``You forgot the oven on!''. Then it is expected that an accident is prevented.

@@

%[David]
The conceptual framework proposed at this work was tested through a reference implementation called \mbox{SmartAndroid} Project\footnote{For more information visit www.tempo.uff.br/smartandroid}. The project includes a programming API to help the developers in constructing UbiApps as well as offers basic management services to provide resource registration, discovery and localization. The SmartAndroid has been developed over Google Android platform as we believe that in a near future it will be widely used in sensors and devices embedded in furnitures and home appliances.
%FIXME: in a near future it will be 
% [we have implemented most of the framework features, thought much more remain to be done]

%proposta de uso de marketplace
% A exposição de dados por meio de \textit{Content Provider} permite a integração de aplicativos externos ao servidor. Estes aplicativos podem ser dispostos em um \textit{marketplace} (http://developer.android.com/distribute/open.html) permitindo que tanto usuários comuns quanto programadores incrementem o ambiente com novas aplicações ubíquas. 
The SmartAndroid middleware contemplates the possility of running multiple applications in the same IE. Thus, focusing on the user and inspired by the Google Play -- which is a application market for Android devices --, we have as a future work the creation of a SmartAndroid Market~\cite{google2013}, where users will be able to easily download and start different applications. Also similar to the Google Play, a Manifest file will require permission for accessing the domains, what will allow users to maintain control over what off-the-shelf applications have permission to know and to do.
% TODO: talk about market place
[security concern on store: helps the discovery of malware before the user download]

  \subsection{Distributed Components Model}
%   [implementation of RA and services]

  [initialization]
%   O SmartAndroid é um aplicativo que inicializa o SGAR, repositório e serviços de comunicação. Este aplicativo deve ser executado em uma única unidade do ambiente, deixando o Deamon de Comunicação em estado de espera até receber requisições de outras aplicações. Em outras unidades (clientes) constam os aplicativos instalados com a biblioteca do SmartAndroid, a qual é necessária para executar o serviço de comunicação e \textit{proxys} dos serviços do SGAR. Assim cada unidade pode consultar sobre IARs, através do SDR, obtendo seus ODARs, cada um com o respectivo RANS, o qual é utilizado pelo \textit{proxy} como referência de acesso.

  [annotation]

@@

@@

  % [main figure]
  \begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/map-forniture-cv-menu-big.pdf}
  \caption{Management and Prototyping Interface} %[IPGAP]
  \label{fig:ipgap}
  \end{figure}
  %FIXME: convert portuguese text to english

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%              SECTION
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example Applications} \label{sec:evaluation}
Some applications have been built to explore the potential of the framework for building UbiApps. Although the example applications are simple, and alone does not justify the deploy of the SmartAndroid in the environment, they have allowed us to validate the features provided by the framework and achieved by the SmartAndroid.

% Among these applications we will

% the SmartLiC, the MediaFollowMe, remote control type applications where resources are controlled remotely by another resource (in this case, a smartphone ), among other applications. A future work is to install a system in Ambi home care health, as in ~ \ cite {} carvalho2010sciads.

  \subsection{Tic-Tac-Toe}
  After the implementations of the basic features of the framework, including the communication mechanisms, we have implemented a distributed Tic-Tac-Too game, where a player can defy another player (or AI player) placed anywhere in the IE. 
  % FIXME: rewrite

%   Nesta seção serão exploradas as questões 1 e 2, relacionadas ao suporte (SGAR) e a aquisição de contexto, através do desenvolvimento de um jogo da velha ubíquo. Esta aplicação é uma adaptação de uma versão simples na plataforma Android, que executa em apenas uma tela, para uma versão \textit{multiplayer}, onde para uma mesma partida cada jogador possui um dispositivo individual para indicar os movimentos efetuados. O objetivo desta adaptação demonstra também a capacidade do \textit{framework} em facilitar a programação de sistemas distribuídos para aplicações inteligentes.

  \subsection{SmartLiC}
  % [smartlic]
  The Smart Light Control (SmartLic) application aims at the clever use of lighting in homes in order to save power consumption, since it is responsible for the largest range of consumption in residential environments. The application uses presence sensors to identify the location of people inside the each room and decide which lamps should be turned on and off. Hence preventing the forgetting of lamps turned on. It also

  % ref to the 'largest range of consumption in residential environments'?

  a control application for residential lighting - that makes the lights of a room being erased as users are absent this

  \subsection{Remote Controls}
  Considering that the users would want to have some control over the resources within the IE, we have implemented the remote controls to interact with them specifically.

  \begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/beagle-lamp.pdf}
  \caption{Remote Control} %[IPGAP]
  \label{fig:remotecontrol}
  \end{figure}

@@

  The \mbox{\textbf{MediaFollowMe}} application enables the user to be followed by any kind of media stream (e.g. video, audio, images) while he/she walks inside the intelligent environment. By the time the user launch the \mbox{MediaFollowMe} app and choose the device which the media stream he wants to be followed, the app will take care of the user's location changes and automatically play, pause or migrate the media to the closest device capable of displaying it.

  To illustrate that, consider a user watching a movie on TV through a blu-ray player in his bedroom. When the user leaves his bedroom, the system identifies this action by an RFID tag and fires an event, as well as when he arrives in any room. As the app is interested in these events, it receives a notification informing that the user left/arrived some room (and which room) and can migrate the media to the proper device, preferable inside that room.

>>>>

% The decentralization of components of the framework (the RAs) follow the principles of the Service-oriented Architecture (SoA), where the more decentralization the more flexibility on connectivity, since the dependence of centralized services is lowered.
%TODO: write it better

@@

    \subsubsection{Security Management Service}
    The security concern is always a central topic on UbiComp systems, due to the diverse aspects of security required. Some aspects are already inherited, depending on the technology adopted, e.g., the \mbox{Wi-Fi} already ensures against the registration of outside devices and the exchange of informations. Thus our proposal for the the SecMS discusses requirements at a higher level, and issues at a lower level are defined according to the platform used.

    % [credentials]
    In UbiComp, any human-machine interaction should be as inconspicuous as possible. However, on what matters to the users there is a need for authentication what may happens through explicit interaction, such as entering a password, fingerprint, eye retina recognition, and so on. Other less intrusive ways are progressing, such as the facial recognition, but this raises privacy issues. The users fit in user groups that restricts their access to domains in the IE. For instance, in a smart home the father and the mother may have administrative permissions, below them there are the other occupants (such as elderly and older children) that have some level of permissions, next the younger children, and lastly the guests.

%     The domains are responsible for grouping UbiApps with the same caracte
%     A domain may represent a set of UbiApps with
    A domain can represent a set of applications that share a common characteristic (e.g., home health care, home surveillance, multimedia), or a set of resource within the same constraints (e.g., adult, children, guest). The SecMS allows modifications on security take effect on the level of middleware. Neither a user can manipulate resources or UbiApps that she has not permission to, nor an application can manipulate resources from outside its domain. The specification of domains complies with the theory of sets, thus an entity may be contained in more than one domain, and so on.

%     On what matters to the users, there is a need to specify roles (or user groups) within the IE~\cite{brush2011home}. These roles would determine  For instance, in a smart home the father and the mother may have more permissions than the others (the administrators), below them there are the other occupants (such as elderly and older children), next the younger children, and lastly the guests.

%     In what concerns to the privacy of the UbiApps, we 
    % [domains]
    % The SecMS manages both the user's credentials and the application's domains.
    % 
    % On the

  \subsection{Context Interpretation} \label{subsec:ci}
%   [motivation]
  Considering the multitude of resources present in the IE, the context interpretation aims at providing a higher level context information hence allowing the reuse of the logic and a separation of concerns. This feature helps to solve the challenge related to the \textit{variety of context information and services}, what is possible via the RA's interfaces, the CVs and OPs.

@@

  An example of context rules has been presented on Figure~\ref{fig:arch}. At the Applications Layer a set of two components implements the interpretation-actuation pattern: the ``Forgotten Stove Interpreter'' and the ``Reminder Actuator'' respectively, where the goal of the rule is to remind the elderly that he has forgotten the oven on while he went to sleep. The former component, which is a CI, is subscribed to two RAs, namely the ``Bed RA'' and the ``Stove RA'' (the dashed arrow means notify subscribers). The latter is subscribed to the CI and calls the RAs, namely the ``TV RA'' and the ``Clock RA'', directly using RPC (represented by the straight arrow). Internally to the CI a rule expression relates the RAs as  ``bed is occupied and oven is turned on for 30 min'', which means that the CI only will be valid if this condition remains true during ``30 min''. When the CI changes its state from invalid to valid (what includes the timing), the subscribers are notified, the ``Reminder Actuator'' in case. This actuator, in its turn, calls the OPs ``fire alarm'' from ``Clock RA'' and ``set message'' from ``TV RA'', with the parameter ``You forgot the oven on!''. Then it is expected that an accident is prevented.

@@

%[David]
The conceptual framework proposed at this work was tested through a reference implementation called \mbox{SmartAndroid} Project\footnote{For more information visit www.tempo.uff.br/smartandroid}. The project includes a programming API to help the developers in constructing UbiApps as well as offers basic management services to provide resource registration, discovery and localization. The SmartAndroid has been developed over Google Android platform as we believe that in a near future it will be widely used in sensors and devices embedded in furnitures and home appliances.
% [we have implemented most of the framework features, thought much more remain to be done]

%proposta de uso de marketplace
% A exposição de dados por meio de \textit{Content Provider} permite a integração de aplicativos externos ao servidor. Estes aplicativos podem ser dispostos em um \textit{marketplace} (http://developer.android.com/distribute/open.html) permitindo que tanto usuários comuns quanto programadores incrementem o ambiente com novas aplicações ubíquas. 
The SmartAndroid middleware contemplates the possility of running multiple applications in the same IE. Thus, focusing on the user and inspired by the Google Play -- which is a application market for Android devices --, we have as a future work the creation of a SmartAndroid Market~\cite{google2013}, where users will be able to easily download and start different applications. Also similar to the Google Play, a Manifest file will require permission for accessing the domains, what will allow users to maintain control over what off-the-shelf applications have permission to know and to do. Within the market, the UbiApp could be tested towards discovering any possible harm that the application could do and any possible inefficiency that could consume too much the energy resources of the host device.
% TODO: talk about market place
% [security concern on store: helps the discovery of malware before the user download]

  \subsection{Location}
  [talk about location]

  \subsection{Communication Support}
  %[talk about stub intantiation calls]
  %TODO: example of CV and OP? Maybe it is worth add some on the text
  To perform any interaction with a RA that is not locally instantiated, the UbiApp must use a stub (also called proxy) that is bound to the referred RA. This stub implements the same interface as the RA, i.e. the same CVs and OPs, which are methods, from a Object-Oriented Programming perspective. With the stub on hands, the application can invoke remote methods, as if they were locally invoked. These remote methods may be to retrieve a CV or to trigger an OP. The Figure~\ref{fig:rpc} represents this direct, or synchronous, communication. The steps to achieve a direct communication, as represented by the figure, are as follows:
  \begin{enumerate}
    \item The UbiApp calls a method from the stub 
    \item The call is forwarded to the RA instance through the network in the second step
    \item This instance can interact with the device (the lamp, in case)
    \item The result or the acknowledge is then returned to the caller
  \end{enumerate}

%     In the first step the UbiApp calls a method from the stub whose call is forwarded to the RA instance throught the network in the sencond step, this instance can interact with the device (the lamp, in case) and return an answer or an aknowledge. In this example, the communication could be used to retrieve come CV status from the lamp such as ``is on'' or ``light intensity''

  \begin{figure}[ht]
  \centering
  \includegraphics[width=1.8in]{figures/comm-rpc.pdf}
  \caption{Direct communication} 
  \label{fig:rpc}
  \end{figure}

  It is possible to acquire the status of a CV directly, however it can also be done indirectly via the pub-sub mechanism, what makes it easier for developers being aware of CV change right away. This indirect, or asynchronous, communication is performed in two stages: the subscription (Figure~\ref{fig:pubsub}.a) and the notification (Figure~\ref{fig:pubsub}.b). During the first stage, represented by the Figure~\ref{fig:pubsub}.a, we have the following steps:
  \begin{enumerate}
    \item The UbiApp sets some RA (``RA X'') to subscribe to another, referred by its RANS (``Lamp RA'') and in a specific CV (``Is on'')
    \item Then the first RA requires to be subscribed to the second, through the network
    \item The second RA accepts the subscription and is bound to the device
  \end{enumerate}

  The second stage happens when the first RA is already subscribed to the second and a notification routine is triggered, what was represented by the Figure~\ref{fig:pubsub}.b and works as follows:
  \begin{enumerate}
    \item The device has its context changed, what may be caused directly (e.g., a user turning the lamp on) or through the RA (i.e. an application, another RA, or rule, calling some RA's OP which caused the change of context)
    \item Then the RA that represents the device notifies all subscribers to that CV (e.g., ``Is on'' from this Lamp RA)
    \item The subscriber may call some callback method of the UbiApp
  \end{enumerate}

  \begin{figure}[ht]
  \centering
  \includegraphics[width=3.4in]{figures/comm-pubsub.pdf}
  \caption{Indirect communication} 
  \label{fig:pubsub}
  \end{figure}

% 
%   \subsection{Distributed Components Model}
% %   [implementation of RA and services]
%   
%   [initialization]
% %   O SmartAndroid é um aplicativo que inicializa o SGAR, repositório e serviços de comunicação. Este aplicativo deve ser executado em uma única unidade do ambiente, deixando o Deamon de Comunicação em estado de espera até receber requisições de outras aplicações. Em outras unidades (clientes) constam os aplicativos instalados com a biblioteca do SmartAndroid, a qual é necessária para executar o serviço de comunicação e \textit{proxys} dos serviços do SGAR. Assim cada unidade pode consultar sobre IARs, através do SDR, obtendo seus ODARs, cada um com o respectivo RANS, o qual é utilizado pelo \textit{proxy} como referência de acesso. 
% 
% 
%   with the RANS 
%   RPC search 
% 
%   
%   [annotation]

@@

  [explain that both the rule expression and the actuator are written in the JSON]

@@

  % [main figure]
  \begin{figure}[ht]
  \centering
  \includegraphics[width=3.5in]{figures/map-forniture-cv-menu-big-v2.pdf}
  \caption{Management and Prototyping Interface} %[IPGAP]
  \label{fig:ipgap}
  \end{figure}
  %FIXME: convert portuguese text to english

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%              SECTION
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example Applications} \label{sec:evaluation}
Some applications have been built to explore the potential of the framework for building UbiApps. Although the example applications are simple, and alone does not justify the deploy of the SmartAndroid in the environment, they have allowed us to validate the features provided by the framework and achieved by the SmartAndroid. It also demonstrated the possibility of concomitant running of UbiApps, what similar to an operation system where different processes run separately but in the same system. Withing the SmartAndroid, UbiApps run separately but in the IE.% and can share resources,

% In this section we will elaborate over the SmartLiC application, and next we will briefly talk about the others.
In the subsections that follows we will elaborate over some UbiApps that have been developed, or are still in development, in the course of the project.
% the SmartLiC, the MediaFollowMe, remote control type applications where resources are controlled remotely by another resource (in this case, a smartphone ), among other applications. A future work is to install a system in Ambi home care health, as in ~ \ cite {} carvalho2010sciads.

  \subsection{Tic-Tac-Toe}
  After the implementations of the basic features of the framework, including the communication mechanisms, we have implemented a distributed Tic-Tac-Too game, where a player can defy another player (or AI player) placed anywhere in the IE. We have used as devices two smartphones.

  In this implementation we have created RAs for both the players and the board. The players subscribe to the board and vice-versa, thus each movement performed by the player is set on the board through RPC, commands from this player are locked and the movement is communicated to the other player, the same happens to the second player, and so on. One of the goals of this implementation was to verify the capability of the framework to make the construction of distributed systems easier.

  \subsection{SmartLiC}
%   primeiramente vc cria um skeleton para a regra
% 
% depois vc pega cada cômodo e de cada um deles faz
  % pega a lampada 
%   pega o sensor de presença
%   cria um CI com a regra e as devidas referencias
%   instancia atuador desligador de lampadas
%   subscreve atuador no ic

  % [smartlic]
  The Smart Light Control (SmartLic) application aims at the clever use of lighting in homes in order to save power consumption, since it is responsible for the largest range of consumption in residential environments. The application uses presence sensors to identify the location of people inside each room, and decide which lamps should be turned on and off. Hence it prevents the forgetting of lamps turned on, and may lit some lamp if a user enters a room at night and if nobody is at sleep in that room. 
  % ref to the 'largest range of consumption in residential environments'?

  The [IPGAP] has allowed us to test this application. We instantiated lamp simulators for each room and an avatar for a user, and also a simulator for day light sensor. Next context rules were created for each room of the house. %Next context rules were created by filling a skeleton of a rule written in json, what caused the instantiation of a CI and actuator for each room.  If the avatar is dragged, in the [IPGAP], from a room and dropped in another, and the specified time passes, the the lamp is turned off.
  \begin{enumerate}
   \item Create a context rule skeleton in JSON
   \item Get the rooms from the house
   \item Get the lamp and presence sensor of each room and fill the rule expression skeleton
   \item Instantiate a CI with the rule expression
   \item Instantiate a actuator to perform the actions declared in the context rule skeleton
   \item Bind the CI and the actuator
   \item Repeat this for each room
  \end{enumerate}

  The event of a user entering some room is triggered when the avatar is dragged from one room and dropped on another. The CI has a timer associated with the expression so, when the rule is valid, the timer is fired. If the context change and the rule is invalidated the timer is stopped, otherwise the evaluation is completed with a valid rule and the subscribers must be notified. Then the actuator turns off the light of the first room.

  There were also rules composed for turning on the light of the room that the user enters if it is day (based on a day light sensor simulator) and if nobody is at sleep in the room (based on another CI).

  Another feature that we will implement is a house security mode, that users may activate if they are travelling or just have left the house alone. The basic operation is to turn lamps on and off as if users were at home, thus deceiving potential thieves. The choices of which lamps to turn on and off will follow the pattern contained in a log file, to mimic a realistic scenario.

  The SmartLiC allowed us to validate two features of the RLS, which are the discovery of the rooms and the RAs of some specific type are within the room (i.e. the lamps and presence sensors). In this UbiApp we also have created a set of context rules with timers using the context rules parser (including CI and actuators). And the [IPGAP] were well explored in this implementation, since we has shown the triggering of many events in parallel and multiple users cohabiting the same IE.
% 
%   After the start of the context rules, 
%   \begin{enumerate}
%    \item On event received, get the sender, the 
%   \end{enumerate}

%   O Código 2 ilustra uma possível implementação da interpretação de contexto pela aplicação \mbox{SmartLiC}. Na etapa de inicialização, a aplicação utiliza o SLR para localizar os cômodos (Linha 2), e obter a lâmpada e o sensor de presença (``lampAR'' e ``presAR'') de cada um, utilizando a busca do SDR (Linhas 4 e 5). Para evitar a repetição do código da regra, suas referências e a respectiva ação a ser desempenhada (desligar a lâmpada referenciada -- ``lampAR.turnOff'') são adicionadas na lista de configurações (``configList'') (Linha 6). A regra é criada em ``rule'' como: ``\mbox{\emph{lâmpada ligada E o cômodo desocupado POR T$_{max}$ unidades de tempo}}'', e desempenha uma relação lógica entre as diferentes VCs e a temporização da regra (Linha 7). Em seguida, subscreve-se às VCs dos ARs de interesse, começando o processamento da regra (Linha 8).

%   Na etapa de avaliação, também descrita no Código 2, é definido um bloco de comando para o tratamento das notificações recebidas dos ARs de interesse (lâmpadas e sensores de presença subscritos). Uma vez recebido um evento com a atualização de uma VC de um dos ARs (``ar\_ref'') (Linha 11), é selecionada a configuração de ``configList'' respectiva (Linha 12). Segue-se a avaliação da regra (\textit{``evaluate}''), utilizando a configuração obtida, e considerando os temporizadores (Linha 13). A etapa de avaliação é bloqueante no caso da existência de temporizadores associados, e a invocação das ações (OPs) ocorre na mesma \textit{thread} que a avaliação. A temporização ocorre enquanto a expressão da regra é válida, se eventos chegarem antes do fim da temporização e isto fizer com que a expressão da regra seja invalidada, então o temporizador é finalizado e as ações não são disparadas.

%   \begin{lstlisting}[caption=Context Interpretation by the SmartLiC, mathescape] 
%   $\textit{//Initialization}$
%   placeList = SLR.getPlaces() $\textit{//Get rooms}$
%   for each place from placeList: $\textit{//Selects a room from the list}$
%       lampAR = SDR.search(Lamp, place) $\textit{//Get lamps from the room}$
%       presAR = SDR.search(Presence, place) $\textit{//Get presence sensor from the room}$
%       configList.add(lampAR, presAR, lampAR.turnOff) $\textit{//Stores configuration}$
%   rule = Lamp.on $\land$ $\lnot$(Presence.occupied) $\land$ T > T$_{max}$ $\textit{//Rule function}$
%   subscribeTo(configList) $\textit{//Subscribes to lamps and presence sensors}$
% 
%   $\textit{//Context rule evaluation}$
%   on event received (ar_ref, vc, value): $\textit{//Notification received}$
%       config = configList(ar_ref, vc) $\textit{//RA configuration selection}$
%       if (evaluate(rule, config)) then: $\textit{//Evaluates rule with configuration}$
% 	  invoke(config.getActions()) $\textit{//Calls action}$
%   \end{lstlisting}

%   \begin{algorithmic}
%   \STATE $asdf$
%   \FORALL{$asdf$ in $asdf$}
%     \STATE $asdf$
%   \ENDFOR
%   
%   \ONEVENT{$(ra, cv, value)$}
%     \STATE $asdf$
%   \ENDEVENT
%   \end{algorithmic}

%   \begin{algorithmic}
%   \STATE $rule \leftarrow Lamp.on \land \lnot(Presence.occupied) \land T > T_{max}$
%   \STATE $placeList \leftarrow RLS.getPlaces()$
%   \FORALL{$place$ in $placeList$}
%     \STATE $lampRA \leftarrow RDS.search(Lamp, place)$
%     \STATE $presRA \leftarrow RDS.search(Presence, place)$
%     \STATE $rule$
%     \STATE $RAs.add(presRA)$
%     \STATE $new ContextInterpreter()$
%   \ENDFOR
%   \STATE $rule \leftarrow Lamp.on \land \lnot(Presence.occupied) \land T > T_{max}$
%   \STATE $subscribeTo(RAs)$
%   \end{algorithmic}
%   
%   
%   \begin{algorithmic}
%   \STATE $placeList \leftarrow RLS.getPlaces()$
%   \FORALL{$place$ in $placeList$}
%     \STATE $lampRA \leftarrow RDS.search(Lamp, place)$
%     \STATE $presRA \leftarrow RDS.search(Presence, place)$
%     \STATE $configList.add(lampRA, presRA, lampRA.turnOff)$
%   \ENDFOR
%   \STATE $rule \leftarrow Lamp.on \land \lnot(Presence.occupied) \land T > T_{max}$
%   \STATE $subscribeTo(configList)$
%   \end{algorithmic}

  \subsection{Remote Controls}
  Considering that the users would want to have some control over the resources within the IE, we have implemented the remote controls to interact with them specifically. The same way that users nowadays have a TV control that enable them to have full control over the device with little effort, using the framework that task will be easily extended to the diverse range of devices present in the IE.

  For implementing a lamp remote control, as shown on the Figure~\ref{fig:remotecontrol}, we are using a prototyping board called BeagleBone~\cite{Beagle2012}. The board, on one side, is capable of turning a lamp on and off and, on the other side, it implements a RA for the lamp which is registered in the IE. A graphical interface of a lamp can remotely call these OPs of the lamp, and it is also subscribed to the Lamp RA, what allows the remote control being aware of the lamp status.

  \begin{figure}[ht]
  \centering
  \includegraphics[width=3.5in]{figures/beagle-lamp.pdf}
  \caption{Remote Control} %[IPGAP]
  \label{fig:remotecontrol}
  \end{figure}

@@

  The \mbox{MediaFollowMe} application enables the user to be followed by any kind of media stream (e.g. video, audio, images) while he walks inside the IE. By the time the user launches the \mbox{MediaFollowMe} application and choose the device in which the media stream he wants to be followed, the application will take care of the user's location changes and automatically play, pause or migrate the media to the closest device capable of displaying it.

  To illustrate that, consider a user watching a movie on a TV through a blu-ray player in his bedroom. When the user leaves his bedroom, the system identifies this action by an RFID tag and fires an event, as well as when he arrives in any room. As the UbiApp is interested in these events, it receives a notification informing that the user has left/arrived some room (and which room) and can migrate the media to the proper device, preferably inside that room.
